Analysis of the included studies

### 2023-06-16 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Loaded jsonlite

```{r}
#' load packages
suppressPackageStartupMessages({
  library('tidyverse')
  library('ggthemes')
  library('scales')
  library('janitor')
  library('countrycode')
  library('bib2df')
  library('conflicted')
  library('ggwordcloud')
  library('here')
  })

>>>>

```{r}
#' load packages
suppressPackageStartupMessages({
  library('tidyverse')
  library('ggthemes')
  library('scales')
  library('janitor')
  library('countrycode')
  library('bib2df')
  library('conflicted')
  library('ggwordcloud')
  library('here')
  library("jsonlite")
  })
